Multi-resolution Neural Field Estimation

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor eits

where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. \parham{This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.} The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}

>>>>

where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$. The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
